Final Paper

### 2016-08-09 eda/business-attributes.Rmd
explanations added to rmds

```{r}
successful_business <- business %>% 
  select(-open) %>% 
  filter(review_count > 300) %>% 
  group_by(state) %>% 
  summarise(num = n())

>>>>

```{r}
# Filters out businesses with more than 300 reviews
# Gets the number of businesses in such category grouping by state.
successful_business <- business %>% 
  select(-open) %>% 
  filter(review_count > 300) %>% 
  group_by(state) %>% 
  summarise(num = n())

### 2016-08-09 eda/location-ratings.Rmd
explanations added to rmds

```{r}
selected_users <- users %>% 
  filter(review_count > 50) %>% 
  select(name, user_id, review_count)

user_reviews <- reviews %>% 
  select(user_id, review_id, stars, business_id)

business_locations <- business %>% 
  select(business_id, state)

user_reviews <- left_join(selected_users, user_reviews) %>% 
  left_join(business_locations) %>% 
  na.omit

familiar_location <- group_by(user_reviews, user_id, state) %>% 
  tally()

location_reviews <- aggregate(n ~ user_id, familiar_location, max) %>%
  left_join(familiar_location) %>% 
  mutate(most_reviewed = TRUE) %>% 
  filter(n > 10) %>% 
  select(-n)

>>>>

```{r}
# Users wrote >= 50 reviews
selected_users <- users %>% 
  filter(review_count > 50) %>% 
  select(name, user_id, review_count)

# Cleaned review data
user_reviews <- reviews %>% 
  select(user_id, review_id, stars, business_id)

# Cleaned business data
business_locations <- business %>% 
  select(business_id, state)

# Selected user data joined with review and business data
user_reviews <- left_join(selected_users, user_reviews) %>% 
  left_join(business_locations) %>% 
  na.omit

# Computed each number of reviews a user wrote in each state
familiar_location <- group_by(user_reviews, user_id, state) %>% 
  tally()

# 
location_reviews <- aggregate(n ~ user_id, familiar_location, max) %>%
  left_join(familiar_location) %>% 
  mutate(most_reviewed = TRUE) %>% 
  filter(n > 10) %>% 
  select(-n)

### 2016-08-09 paper/paper.Rmd
explanations added to rmds

####Stage Two: Data Wrangling
We began by filtering for businesses with more than 300 reviews in the United States. Looking more closely at the business dataset, we noticed a nested data-frame of attributes for each business, so we cleaned and gathered the data so that each row contained one business attribute. Business data set was used to see what makes a business popular and successful; especially by looking at where most-reviewed are clustered and the influence of major business attributes.
```{r load_business, echo = FALSE}
business <- read_csv("../clean_data/yelp_business.csv")
names(business) <- c("business_id", "open", "categories", "count", "state", "stars", "noise", "attire", "Take-out", "Takes Reservation", "Offers Delivery", "Outdoor Seating", "Accepts Credit Card", "Happy Hour")
successful_business <- business %>% 
  select(-open) %>% 
  filter(count > 300) %>% 
  group_by(state) %>% 
  summarise(num = n())
```
Review data was cleaned for sentiment analysis using a library called “tidytext”. After reading in the review dataset, we randomly sampled 500,000 observations. With this, we tokenized each word in a text review into a single row in the data-frame and removed stop words like “a”, “and”, “the”, etc. since they had no indication of the reviewers’ attitudes. Using built-in lexicons, we assigned each word a valence score and computed the mean score for each review. Additionally, we created per-word summaries, computing the number of business and reviews the word appeared in and the average star rating based on each review. We filtered for words that appeared in more than 10 businesses and 500 reviews to exclude rare words with strange valence scores and ratings. Using these cleaned datasets, we were able to create visualizations and make inferences discussed later.

@@

Instead, we ended up with a bar graph, which clearly shows which state has the most number of businesses with over 300 reviews. There were 6 distinct regions in total. Interestingly, the graph shows that the majority of the businesses is located in two states: about 62% of the filtered businesses were located in Nevada and another 31% was in Arizona. 
```{r business, echo = FALSE, fig.align = "center"}
ggplot(successful_business, aes(x = reorder(state, -num), 
                                y= num)) + 
  geom_bar(stat = "identity", 
           position = "dodge") +
  xlab("State") + 
  ylab("Number of Businesses") +
  theme(text = element_text(family = "Times New Roman"))
```

@@

```{r wordcloud, echo = FALSE, message = FALSE, fig.height = 3.5}
reviews_text <- read_csv("../clean_data/reviews_text.csv")
one <- reviews_text %>% 
  filter(stars == 1) %>% 
  group_by(word) %>% 
  count() %>% 
  top_n(100) %>% 
  arrange(n)

five <- reviews_text %>% 
  filter(stars == 5) %>% 
  group_by(word) %>% 
  count() %>% 
  top_n(100) %>% 
  arrange(n)

>>>>

####Stage Two: Data Wrangling
We began by filtering for businesses with more than 300 reviews in the United States. Looking more closely at the business dataset, we noticed a nested data-frame of attributes for each business, so we cleaned and gathered the data so that each row contained one business attribute. Business data set was used to see what makes a business popular and successful; especially by looking at where most-reviewed are clustered and the influence of major business attributes.
```{r load_business, echo = FALSE}
business <- read_csv("../clean_data/yelp_business.csv")
names(business) <- c("business_id", "open", "categories", "count", "state", "stars", "noise", "attire", "Take-out", "Takes Reservation", "Offers Delivery", "Outdoor Seating", "Accepts Credit Card", "Happy Hour")
successful_business <- business %>% 
  select(-open) %>% 
  filter(count > 300) %>% 
  group_by(state) %>% 
  summarise(num = n())
ratings_business <- business %>% 
  select(business_id, state, stars, count)
```
Review data was cleaned for sentiment analysis using a library called “tidytext”. After reading in the review dataset, we randomly sampled 500,000 observations. With this, we tokenized each word in a text review into a single row in the data-frame and removed stop words like “a”, “and”, “the”, etc. since they had no indication of the reviewers’ attitudes. Using built-in lexicons, we assigned each word a valence score and computed the mean score for each review. Additionally, we created per-word summaries, computing the number of business and reviews the word appeared in and the average star rating based on each review. We filtered for words that appeared in more than 10 businesses and 500 reviews to exclude rare words with strange valence scores and ratings. Using these cleaned datasets, we were able to create visualizations and make inferences discussed later.

@@

Instead, we ended up with a bar graph, which clearly shows which state has the most number of businesses with over 300 reviews. There were 6 distinct regions in total. Interestingly, the graph shows that the majority of the businesses is located in two states: about 62% of the filtered businesses were located in Nevada and another 31% was in Arizona. 
```{r business, echo = FALSE, fig.align = "center",message = FALSE, fig.height = 3.5}
ggplot(ratings_business,aes(x=stars, y=count)) +  
  geom_point(col = rgb(0,0,1,0.25), pch = 16, cex = 2) +
  scale_y_continuous(limits=c(300,5000)) +
  xlab("Star Ratings") + 
  ylab("Review Counts") +
  theme(text = element_text(family = "Times New Roman"))

ggplot(successful_business, aes(x = reorder(state, -num), 
                                y= num)) + 
  geom_bar(stat = "identity", 
           position = "dodge") +
  xlab("State") + 
  ylab("Number of Businesses") +
  theme(text = element_text(family = "Times New Roman"))
```

@@

```{r wordcloud, echo = FALSE, message = FALSE, fig.height = 3.5}
reviews_text <- read_csv("../clean_data/reviews_text.csv")
one <- reviews_text %>% 
  filter(stars == 1) %>% 
  group_by(word) %>% 
  tally() %>% 
  top_n(100) %>% 
  arrange(n)

five <- reviews_text %>% 
  filter(stars == 5) %>% 
  group_by(word) %>% 
  tally() %>% 
  top_n(100) %>% 
  arrange(n)
